Fuzzy joins through deep learning

### 2018-07-27 paper2018/siamese_networks.tex
added another figure

\begin{figure}
\includegraphics[width=1.0\linewidth]{schroff_triplet}
\caption{Triplet loss}
\label{schroff_loss}
\end{figure}

@@

\subsubsection{Improved Loss}
 An improvement over the triplet loss function is proposed by \cite{DBLP:conf/cvpr/SchroffKP15} for the recognition of faces in videos \cite{Zhang:2016:DML:3088616.3088665}.  Conceptually, this function that we refer to as `improved loss' in the paper considers the distances from the \textit{positive} element of the triplet to the \textit{negative} element as well, and tries to maximize that difference as well as the distance from \textit{anchor} to the \textit{negative}.  In addition,it corrects the fact the  original triplet loss function has no constraints on how close the positive distance should be.  For instance, it is possible for the \textit{anchor} and \textit{positive} form a large cluster with a large intra-class distance. The equations that achieve these constraints are described below.  Equation~\ref{psi} tries to reduce intra-class distance by ensuring it is less than $\hat{\alpha}$.  Equation~\ref{phi} tries to maximize inter-class distance by ensuring that the distance from the \textit{anchor} and \textit{positive} to the negative are both taken into account.  Equation~\ref{improved_loss} balances inter-class constraints with intra-class constraints with the parameter $\lambda$.

>>>>

\begin{figure}
\includegraphics[width=0.5\linewidth]{schroff_triplet}
\caption{Triplet loss}
\label{schroff_loss}
\end{figure}

@@

\subsubsection{Improved Loss}

\begin{figure}
\includegraphics[width=0.5\linewidth]{modified_loss}
\caption{Modified loss}
\label{modified_loss}
\end{figure}

 An improvement over the triplet loss function is proposed by \cite{DBLP:conf/cvpr/SchroffKP15} for the recognition of faces in videos \cite{Zhang:2016:DML:3088616.3088665}.  Conceptually, this function that we refer to as `improved loss' in the paper considers the distances from the \textit{positive} element of the triplet to the \textit{negative} element as well, and tries to maximize that difference as well as the distance from \textit{anchor} to the \textit{negative}.  In addition,it corrects the fact the  original triplet loss function has no constraints on how close the positive distance should be.  For instance, it is possible for the \textit{anchor} and \textit{positive} form a large cluster with a large intra-class distance. The equations that achieve these constraints are described below.  Equation~\ref{psi} tries to reduce intra-class distance by ensuring it is less than $\hat{\alpha}$.  Equation~\ref{phi} tries to maximize inter-class distance by ensuring that the distance from the \textit{anchor} and \textit{positive} to the negative are both taken into account.  Equation~\ref{improved_loss} balances inter-class constraints with intra-class constraints with the parameter $\lambda$.
